### 2016-01-16 paper.tex
Clean up torque arm description
Minor edits to synchronization paragraph

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells. The turbine
shaft RPM was controlled by a servo motor system, which allowed precise control
of the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer. A load cell mounted at a fixed distance from the servo motor,
provides a redundant measurement. Turbine shaft angle was measured using the
servo drive's emulated encoder output, set to $10^5$ counts per turbine shaft
revolution. Carriage speed, and therefore inflow velocity was measured using a
linear encoder with 10 $\mu$m resolution. All of these performance-related
quantities were sampled at 2 kHz, while the tow tank's motion controller
provided redundant measurements of the carriage speed turbine angular velocity
sampled at 1 kHz. Turbine wake measurements at 1 meter downstream were measured
with a Nortek Vectrino+ acoustic Doppler velocimeter, sampling at 200 Hz. A
photo and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.

@@

\paragraph{Synchronization.} The three data acquisition instrumentation
subsystems---motion controller, NI DAQ (performance measurements), and Vectrino+
(wake velocity measurements)---started sampling at precisely the same time each
tow, after being triggered by a TTL pulse created by the motion controller. This
strategy retained synchronization for all performance signal samples (tow speed,
torque, drag, angular velocity), ensuring precise calculation of, e.g., power
coefficient. Since there is also synchronization of the initial sample from each
three subsystems, correlation of events in the performance and wake signals is
also possible.

>>>>

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells. The turbine
shaft RPM was controlled by a servo motor system, which allowed precise control
of the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer. A load cell mounted at a fixed distance from the servo motor
via a moment arm provided a redundant torque measurement. Turbine shaft angle
was measured using the servo drive's emulated encoder output, set to $10^5$
counts per turbine shaft revolution. Carriage speed, and therefore inflow
velocity was measured using a linear encoder with 10 $\mu$m resolution. All of
these performance-related quantities were sampled at 2 kHz, while the tow tank's
motion controller provided redundant measurements of the carriage speed turbine
angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
sampling at 200 Hz. A photo and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.

@@

\paragraph{Synchronization.} The three data acquisition instrumentation
subsystems---motion controller, NI DAQ (performance measurements), and Vectrino+
(wake velocity measurements)---started sampling at precisely the same time each
tow, after being triggered by a TTL pulse created by the motion controller. This
strategy retained synchronization for all performance signal samples (tow speed,
torque, drag, angular velocity), ensuring precise calculation of, e.g., power
coefficient. Since there was also synchronization of the initial sample from
each of the three subsystems, correlation of events in the performance and wake
signals is also possible.
